On the application of microwave acoustic resonant viral inactivation \thanks{I would be delighted to include any criticisms or comments anyone may have; preferably leave them on the GitHub issues page, or email therobotist@gmail.com, @0xDBFB7 on Twitter, or irc.0xDBFB7.com:6667 \#covid.}

### 2020-07-17 documents/paper.tex
Enough bibtex. Let's go back to hardware.

%\bibliographystyle{plainnat}

@@

\cite{frohlichLongrangeCoherenceEnergy1968} \textrightarrow \ \cite{frohlichBiologicalEffectsMicrowaves1980} \textrightarrow \ (\cite{hungFocusingReflectarrayIts2014} $\parallel$ \cite{yangEfficientStructureResonance2015} $\parallel$ \cite{sunResonantDipolarCoupling2017})\footnote{We have not conducently unlike human cellular structures, as we shall see} - coincidentally have just the right size, shape, stiffness, and net charge distribution to form a weak (Q=2) spherical dipole resonance mode which couples well to the microwave spectrum at approximately 8 GHz.

@@

A poignant summary of the consensus is found in \cite{instituteofelectricalandelectronicsengineersIEEEC95120052006}, Annex B, "Identification of levels of RF exposure responsible for adverse effects: summary of the literature".

>>>>

@@

We've got a thing 
that's called 
Radar Love
We've got a wave
in the air

The phased-array techdemo.

\paragraph{{\Large the gist}}\

The chain of literature 
%
\cite{Longrange1968} \textrightarrow \ \cite{Biological1980} \textrightarrow \ [Liu 2009] \textrightarrow \ ([Hung 2014] $\parallel$ [Yang 2015] $\parallel$ [Sun 2017])\footnote{We have not conducted a thorough review; many more papers are probably involved.} apparently culminates in the flagship work we focus on in this paper,

{\it Efficient Structure Resonance Energy Transfer from Microwaves to Confined Acoustic Vibrations in Viruses} [Yang 2015].
%

which establishes that - unique to certain viruses, and apparently unlike human cellular structures, as we shall see - coincidentally have just the right size, shape, stiffness, and net charge distribution to form a weak (Q=2) spherical dipole resonance mode which couples well to the microwave spectrum at approximately 8 GHz.

@@

A poignant summary of the consensus is found in \cite{IEEE2006}, Annex B, "Identification of levels of RF exposure responsible for adverse effects: summary of the literature".
